\section{Introduction}\label{sec:introduction}

Access to adequate sanitation is a fundamental right.
Yet, it remains out of reach for large portions of the population in low-income urban areas worldwide.
In Brazil, the 2022 Census showed that 24.3\% of the population still relies on precarious sanitation methods, with sanitation deficits concentrated in peripheral and informal settlements \cite{IBGE2024censo}.
The consequences are well documented: inadequate sanitation is associated with diarrheal disease, soil-transmitted infections, and broader public health burdens that disproportionately affect the most vulnerable communities \cite{PrssUstn2019}.
Expanding sanitation coverage in these contexts depends not only on political will and investment, but also on the technical capacity to plan collection networks efficiently and at a low cost.

Planning a sewage collection network is a technically complex task.
It requires analyzing the road network, modeling flow based on terrain elevation, estimating sewage contribution per lot, and defining a viable layout for the collector network.
Approaches based on graph theory have been explored in the literature for layout generation and optimization of sewer systems \cite{Turan2019}, demonstrating that a computational formulation of the problem can substantially reduce manual effort.
In practice, however, this kind of computational support is typically delivered through specialized commercial software, which requires licensing costs and technical infrastructure that are often unavailable to small municipalities, social organizations, and engineering professionals operating in underserved communities.

This paper presents \method, an open-source web system designed to support preliminary planning of sewage collection networks in low-income areas.
\method combines graph-based modeling of the road and collector network, automatic topographic enrichment from public elevation data, interactive graph editing, and a deep learning module for building detection from satellite imagery.
\mirela{Mencionar FELL 1.}
The system operates entirely on open data sources and open-source software.
The result is a tool that brings computational support to the early stages of sanitation planning, where decisions about network layout and feasibility have the greatest impact.

The main contributions of this work are:
(i) a graph-based pipeline for automatic generation of candidate sewage collector layouts from OpenStreetMap data and digital elevation models;
(ii) an interactive web interface that allows domain experts to refine the generated network before and after algorithmic processing;
(iii) a building detection module using DL to improve sewage contribution estimates;
and (iv) a case study on a real low-income urban area comparing URBANUS-assisted planning time against manual expert-based planning, revealing a reduction from an estimated six months of work to approximately 41 seconds of processing time.

The paper is organized as follows:
Section \ref{sec:background} presents the background concepts.
Section \ref{sec:related_work} discusses related work.
Section \ref{sec:proposal} introduces the proposed method \method.
Section \ref{sec:experiments} presents the experimental validation.
Finally, Section \ref{sec:conclusions} gives the conclusions.

