\section{Conclusions}\label{sec:conclusions}

This paper presented \method, an open-source web platform for preliminary planning of sanitary sewer collection networks in low-income urban areas.
\method combines graph-based modeling of street and collector network, automatic topographic enrichment from public elevation data, interactive graph editing, and a DL module for building detection from satellite imagery.

The system is under active development.
On the algorithmic side, the manhole clustering and alignment refinement steps will be extended to handle denser and more irregular street configurations.
The building detection module will be more tightly integrated into the main pipeline, enabling sewage contribution estimates to be computed automatically, avoiding manual lot-by-lot input.
Future work includes per-lot instance counting and classification of individual buildings, which will enable sewage contribution estimates at finer granularity.
Hybrid CNN-Transformer architectures and multimodal fusion strategies with digital surface models (DSM) will also be investigated to improve accuracy in high-density urban scenarios~\cite{zhou2024hierarchical}.

\mirela{Falar que é um trabalho preliminar, que deve ser validado em regiÕes e terrenos com características heterogêneas.}

On the validation side, the system will be evaluated on other municipalities with distinct topographic and urban  morphology profiles.
We aim to have a more comprehensive assessment of generalization across different urban contexts.
By lowering the technical and financial barriers to sanitation planning, \method aims to support engineers, municipalities, and policymakers in expanding sewer coverage to the communities that need it most.
