\documentclass[12pt]{article}

\usepackage{sbc-template}
\usepackage{graphicx,url}
\usepackage[utf8]{inputenc}
% \usepackage[brazil]{babel}
% \usepackage[latin1]{inputenc}  
% \usepackage{float}
\usepackage{xspace}
\usepackage{xcolor}
 
\input{dfn}
     
\sloppy

\title{Supporting sanitation infrastructure planning in\\low-income areas with URBANUS}

\author{Maria do Carmo O. Correia\inst{1,2}, Erick P.A. Barcelos\inst{1},
    Augusto C. B. Pereira\inst{1},\\
    Gerson Seluque Ferreira\inst{2}, Mirela T. Cazzolato\inst{1}}

\address{Institute of Mathematics and Computer Science -- University of São Paulo (USP)
\\
    Av. Trabalhador São-carlense, 400 - Centro, 13566-590 -- São Carlos, SP -- Brazil
\nextinstitute
    SELCO Arquitetura e Engenharia Ltda -- Ribeirão Preto, SP -- Brazil
    \email{carmem@selco.com.br, brcls@usp.br}
    \email{augustocbp@usp.br, gerson@selco.com.br, mirela@icmc.usp.br}
}

\begin{document} 
 
\maketitle

\begin{abstract}
Access to sanitation infrastructure remains a critical challenge in low-income urban areas, with direct consequences for public health and social equity.
We propose \method, a web-based decision-support platform that automates the preliminary design of sanitary sewer collection networks using publicly available geospatial data.
The system models the urban street network as a graph, enriches vertices with topographic elevation, and applies a gravitational routing heuristic (RSPH) to generate a directed sewer network aligned with terrain constraints.
An interactive editor allows specialists to inspect and adjust the graph before processing, keeping human expertise inside the computational workflow.
A deep learning module for building detection from satellite imagery, based on fine-tuned models, enables accurate sewage contribution estimates per lot.
A use case with a Brazilian municipality reduced the domain expert work from days to seconds.
\method aims to support engineers, municipalities, and policymakers in expanding coverage to underserved communities.
\end{abstract}

\input{sections/1.introduction}
\input{sections/2.background}
\input{sections/3.related_work}
\input{sections/4.methodology}
\input{sections/5.experiments}
\input{sections/6.conclusions}

\section*{Acknowledgments}

This work was supported by the São Paulo Research Foundation (FAPESP -- grants \#2026/11130-2, \#2024/15430-5, \#2024/13328-9), the Coordination for Higher Education Personnel Improvement (CAPES -- Finance Code 001), the National Research Council (CNPq and PIBIC 2025-3154), and the University of São Paulo (PRPI 1032 - grant \#207). 

\bibliographystyle{sbc}
\bibliography{references}

\end{document}
